Stack Safety is a Security Property

### 2021-04-17 tex/main.tex
Nits

First, they eliminate the initialization pass. In the {\em Lazy Tagging}
system, the stack is initially tagged as \(\tagNoDepth\),
\rb{The previous section already presents ``unused'' as the default tag,
  though it doesn't say that it can be overwritten whenever\apt{but see my
    query re the HEADER\_NO\_INIT bug}}\sna{Correct there, but now I'm talking
  about laziness.}
A function is permitted
to overwrite clear memory, and when it does so its depth tag overwrites
the clear tag, claiming the memory; the remainder of the policy functions
as {\em Depth Isolation}. On return, the callee must clear its frame, restoring
it to \(\tagNoDepth\), which is still a heavy cost.

@@

\paragraph{Formalization of variable passing.}
We add extra information to our call
annotations to reflect that they may now pass variables on the stack, and that the locations
of those variables may be dynamic (as in the case of pass-by-reference).
A call annotation now includes a predicate relating machine states to the components
that should be passed---when passing by value, this will typically be freshly allocated
cells at the top of the frame, while passing by reference just gives the
addresses of the appropriate variables.\apt{This still doesn't make sense to me. We cannot
  give a static annotation that identifies the absolute address of a stack-allocated variable!
  Only sp-relative addresses make sense.}

@@

Now we can inductively define the context update function; these rules again apply in the order
presented. \bcp{Too much space between the second and third.}

@@

There are several proposals around the use of Cheri capabilities to enforce stack safety,
ranging from mechanisms that use the standard Cheri hardware (which includes local
capabilities) \citep{SkorstengaardLocal},
to those that propose entirely new types of capabilities, such as linear
\citep{SkorstengaardSTK}, uninitialized \citep{Georges+21}, lifetime \citep{Tsampas+19}, and monotonic \citep{GeorgesComplete}.
Of these, uninitialized capabilities seem particularly promising---they naturally enforce
write-before-read behavior, and therefore will enable confidentiality without the need
to clear large swaths of the stack. We propose to implement a model of the stack safety
system described in \citet{Georges+21} and test it against our properties using
QuickChick.

>>>>

First, they eliminate the initialization pass. In the {\em Lazy Tagging}
system, the stack is again initially tagged as \(\tagNoDepth\),
%\rb{The previous section already presents ``unused'' as the default tag,
%  though it doesn't say that it can be overwritten whenever\apt{but see my
%    query re the HEADER\_NO\_INIT bug}}\sna{Correct there, but now I'm talking
%  about laziness.}\leo{Should be better now}
A function is permitted
to overwrite clear memory, and when it does so its depth tag overwrites
the clear tag, claiming the memory; the remainder of the policy functions
as {\em Depth Isolation}. On return, the callee must clear its frame, restoring
it to \(\tagNoDepth\), which is still a heavy cost.

@@

\paragraph{Formalization of variable passing.}
We add extra information to our call
annotations to reflect that they may now pass variables on the stack, and that the locations
of those variables may be dynamic (as in the case of pass-by-reference).
A call annotation now includes a predicate relating machine states to the components
that should be passed---when passing by value, this will typically be freshly allocated
cells at the top of the frame, while passing by reference just gives the
addresses of the appropriate variables relative to the stack pointer.
\apt{This still doesn't make sense to me. We cannot
  give a static annotation that identifies the absolute address of a stack-allocated variable!
  Only sp-relative addresses make sense.}\leo{Better now? :)}

@@

Now we can inductively define the context update function; these rules again apply in the order
presented. \ifspace\bcp{Too much space between the second and third.}\fi

@@

There are several proposals around the use of Cheri capabilities to enforce stack safety,
ranging from mechanisms that use the standard Cheri hardware (which includes local
capabilities) \citep{SkorstengaardLocal},
to those that propose entirely new types of capabilities, such as linear
\citep{SkorstengaardSTK}, uninitialized \citep{Georges+21}, lifetime \citep{Tsampas+19}, and monotonic \citep{GeorgesComplete}.
Of these, uninitialized capabilities seem particularly promising---they naturally enforce
write-before-read behavior, and therefore will enable confidentiality without the need
to clear large swaths of the stack. We plan to implement a model of the stack safety
system described in \citet{Georges+21} and test it against our properties using
QuickChick.
